Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-10-28 WSSSPE3/report/wg_main_industry_interaction.tex
small fixes and comments in industry interactions section

We characterize each of these potential changes in funding as "transition pathways" to sustainable software (see similar work by Geels and Schot, 2007).

At WSSSPE 3 our group was interested in better understanding successful pathways for scientific software to "transition" from government-funded research projects to industry sponsorship. (This may be an initially awkward phrase - because some software projects will begin their life being sponsored by industry, or result in collaboration between industry and academia. In such cases, there is still a need to understand how IP and how maintenance of the software is sustained over time)

Although transitions iare often studied under the broad umbrella of 'technology transfer' we believe there are likely to be a number of different ways in which a pathway from initial production to long-term maintenance and secure funding is achieved. In short, industry sponsorship is an important aspect of sustaining scientific software, but our current understanding of these transitions focuses narrowly on commercial successes / failures.

@@

\begin{itemize}
\item REF Impact Case Studies: http://impact.ref.ac.uk/CaseStudies/
\item Background of projects funded in the UK: http://gtr.rcuk.ac.uk/ 
\item Dowling Review from the UK - addresses complexity of work between these two communities: http://www.raeng.org.uk/policy/dowling-review 
\item Pathway to Impact - UK report  - 2 pages of grant proposals are asked to forecast how they might impact (includes environmental, academic, economic )
\end{itemize}

@@

Our work at WSSSPE 3 included the following activities (described in detail below): 1. Brainstorming goals for this type of research, 2. Imagining potential outcomes of completing a set of case studies on this topic, and 3. Generating a set of working definitions for some of the broad concepts we are describing.

@@

Complete a set of case studies which look at successful and unsuccessful transitions between academic researchers and industry. This might address one of each of the transition types (described below). Succesful transitions are described as those that lead to either weak or strong sustainability (also defined below).

@@

\begin{itemize}
\item Handoff model - i.e. academia initially writes the software, industry (for profit or nonprofit) then takes over project. 
\item Co-Production Model - i.e. industry and academia interact throughout development of the project.
\item Sponsorship Model  - i.e. academia writes and maintains the software, the industry contributes funding for the development/maintenance of software. In this example industry is also likley a user of the software.
\item Spinoff model- transition to For-profit company owned by or in collaboration original developers; or, Non-profit formed by or in collaboration with developers. 
\end{itemize}

@@

\begin{itemize}
\item Weak Sustainability: Software continues to be accessible, useful, and usable. 
\item Strong Sustainability: Software meets criteria above, but is also able to be reused for further innovation (i.e. issued non-restrictive open-source license). (see Becker et al., 2014 for extended discussion of weak vs. strong sustainability.)
\end{itemize}

@@

\subsection{Works Referrenced}

>>>>

We characterize each of these potential changes in funding as ``transition pathways'' to sustainable software (see similar work by Geels and Schot, 2007).

At WSSSPE 3 our group was interested in better understanding successful pathways for scientific software to ``transition'' from government-funded research projects to industry sponsorship. (This may be an initially awkward phrase - because some software projects will begin their life being sponsored by industry, or result in collaboration between industry and academia. In such cases, there is still a need to understand how IP and how maintenance of the software is sustained over time)

Although transitions are often studied under the broad umbrella of `technology transfer' we believe there are likely to be a number of different ways in which a pathway from initial production to long-term maintenance and secure funding is achieved. In short, industry sponsorship is an important aspect of sustaining scientific software, but our current understanding of these transitions focuses narrowly on commercial successes / failures.

@@

\begin{itemize}
\item REF Impact Case Studies: \url{http://impact.ref.ac.uk/CaseStudies/}
\item Background of projects funded in the UK: \url{http://gtr.rcuk.ac.uk/}
\item Dowling Review from the UK - addresses complexity of work between these two communities: \url{http://www.raeng.org.uk/policy/dowling-review}
\item Pathway to Impact - UK report  - 2 pages of grant proposals are asked to forecast how they might impact (includes environmental, academic, economic )
\end{itemize}

@@

Our work at WSSSPE3 included the following activities (described in detail below): 1. Brainstorming goals for this type of research, 2. Imagining potential outcomes of completing a set of case studies on this topic, and 3. Generating a set of working definitions for some of the broad concepts we are describing.

@@

Complete a set of case studies which look at successful and unsuccessful transitions between academic researchers and industry. This might address one of each of the transition types (described below). Successful transitions are described as those that lead to either weak or strong sustainability (also defined below).

@@

\begin{itemize}
\item Handoff model - i.e., academia initially writes the software, industry (for profit or nonprofit) then takes over project. 
\item Co-Production Model - i.e., industry and academia interact throughout development of the project.
\item Sponsorship Model  - i.e., academia writes and maintains the software, the industry contributes funding for the development/maintenance of software. In this example industry is also likely a user of the software.
\item Spinoff model- transition to for-profit company owned by or in collaboration original developers; or, non-profit formed by or in collaboration with developers. 
\end{itemize}

@@

\begin{itemize}
\item Weak Sustainability: Software continues to be accessible, useful, and usable. 
\item Strong Sustainability: Software meets criteria above, but is also able to be reused for further innovation (i.e., issued non-restrictive open-source license). (see Becker et al., 2014 for extended discussion of weak vs. strong sustainability.)
\end{itemize}

@@

\todo{where should someone go who want to know more about this and perhaps wants to contribute?}

\subsection{Works Referenced}

\todo{please add these to the bib file and cite them from there.}
